DRAFT: Social Learning and Shared Belief: The Importance of Bias and Trust for Information Diffusion

### 2014-07-12 paper/paper.tex
local changes
finish fixing posteriors
fix full conditional

\[p(\gamma_i | \mu, \xi^2) = N(\mu, \xi^2I)\]

\[p(\alpha_{it} | \text{\boldmath$\alpha$}_{t-1}. \gamma_i, \delta^2) = N(\text{\boldmath$\alpha$}^T_{t-1} \gamma_i, \delta^2I)\]

\[p(\beta_t | \beta_{t-1}, \sigma^2) = N(\beta_{t-1}, \sigma^2I)\]

\[p(\theta | \alpha_{it}, a^2) = N(\alpha_{it}, a^2I)\]

\[p(\phi | \beta_t, b^2) = N(\beta_t, b^2I)\]

@@

\[p(\theta, \phi, \gamma_i, \alpha_{it}, \beta_t, z | w) \propto p(w | \phi, z) p(\phi |  \beta_t, b^2)  p(z | \theta)  p(\beta_t | \beta_{t-1}, \sigma^2) p(\theta | \alpha_{it}, a^2) p(\alpha_{it} | \text{\boldmath$\alpha$}_{t-1}, \gamma_i, \delta^2) p(\gamma_i | \mu, xi^2)\]

@@

\[= \frac{\theta_{it}^{I_{z_{jit}}=k}}{\sum_k \theta_{it}} \frac{\phi_{kt}^{I_{w_j}=v}}{\sum_v \phi_{kt}}\]

@@

@@

>>>>

\[p(\gamma_i | \mu, \xi^2) = N(\eta, \xi^2)\]

\[p(\alpha_{it} | \text{\boldmath$\alpha$}_{t-1}, \gamma_i, \delta^2) = N(\text{\boldmath$\alpha$}^T_{t-1} \gamma_i, \delta^2)\]

\[p(\beta_t | \beta_{t-1}, \sigma^2) = N(\beta_{t-1}, \sigma^2)\]

\[p(\theta | \alpha_{it}, a^2) = N(\alpha_{it}, a^2)\]

\[p(\phi | \beta_t, b^2) = N(\beta_t, b^2)\]

\[p(a^2 | \nu_0, \tau_0) = IW(\nu_0, \tau_0)\]

\[p(b^2 | \nu_1, \tau_1) = IW(\nu_1, \tau_1)\]

@@

\[p(\theta, \phi, \gamma, \alpha, \beta, z | w) \propto \prod_{t=1}^T \prod_{i=1}^N \prod_{d=1}^{D_i} \prod_{j=1}^{J_d} \prod_{k=1}^K p(w_{jit} | \phi_k, z_{jit}) p(\phi_k | \beta_t, b^2) p(b^2 | \nu_1, \tau_1) p(z_{jit} | \theta_{dit}) p(\beta_t | \beta_{t-1}, \sigma^2) p(\theta_{dit} | \alpha_{it}, a^2) p(\alpha_{it} | \text{\boldmath$\alpha$}_{t-1}, \gamma_i, \delta^2) p(\gamma_i | \eta, xi^2)\]

@@

\[= \frac{\theta_{it}^{I_{z_{jit}}=k}}{\sum_k \theta_{it}} \frac{\phi_{t}^{I_{w_{jit}}=v}}{\sum_v \phi_{kt}}\]

@@

\subsection{Posterior Specification for $b^2$}

\[p(b^2|\beta,\phi) \propto \prod_{t=1}^T \prod_{k=1}^K p(\phi_{kt} | \beta_t, b^2)p(b^2 | \nu_0, \tau_0) \]

\[= \prod_{t=1}^T \prod_{k=1}^K N(\phi_{kt};\beta_t, b^2)IW(\nu_0, \tau_0)\]

\[\propto IW\left(\nu_0 + TK, \left(\tau_0 + \sum_{t=1}^T \sum_{k=1}^K (\phi_{kt} - \beta_t)(\phi_{kt} - \beta_t)^T\right)^{-1}\right)\]

@@

\subsection{Posterior Specification for $a^2$}

\[p(a^2|\alpha,\theta) \propto \prod_{t=1}^T \prod_{i=1}^N \prod_{d=1}^{D_i} p(\theta_{dit} | \alpha_{it}, a^2)p(a^2 | \nu_1, \tau_1) \]

\[= \prod_{t=1}^T \prod_{i=1}^N \prod_{k=1}^K N(\theta_{dit};\alpha_{it}, a^2)IW(\nu_1, \tau_1)\]

This needs to be fixed

\[\propto IW\left(\nu_1 + TND, \left(\tau_0 + \sum_{t=1}^T \sum_{i=1}^N \sum_{d=1}^{D_i} (\theta_{dit} - \alpha_{it})(\theta_{dit} - \alpha_{dit})^T\right)^{-1}\right)\]
